---
title: "Analysis"
author: "Pablo Pavan"
date: "November 30, 2018"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## load the library

```{r}
library(gridExtra)
library(readr)
library(ggplot2)
library("dplyr", lib.loc="~/R/x86_64-pc-linux-gnu-library/3.4")
library("tidyr", lib.loc="~/R/x86_64-pc-linux-gnu-library/3.4")
```
## Functions 2kn

```{r}

selected_values <- function(data, A, B, C, D){
    # Default Options equal -1 on table
      ly <- 1
      ne <- 2
      la <- 0
      ap <- 0.01

    # Other Options equal 1 on table
      if(A==1){
        ly <- 4
      }  
      
      if(B==1){
        ne <- 16
      } 

      if(C==1){
        la <- 0.1
      } 

      if(D==1){
        ap <- 0.1
      } 

      # The data can have other measurements, filter it
      value <- data %>% filter(layers==ly,
                             neurons==ne,
                           lambda==la,
                             alpha==ap) 

      return(list(value$Mean, value$Sd))

}


alloc_vari_4_fact <- function(data){
    # Values for the signs table
    x <- seq(-1, 1, 2)


    
    data %>% group_by(layers, neurons, lambda, alpha) %>% 
         summarize(N=n(), Mean=mean(f1_mean), Sd=sd(f1_mean)) -> data_mean
    
    print(data_mean)

    d1 <- expand.grid(A = x, B = x, C = x, D = x)
    d1 %>% rowwise() %>% mutate(AB=A*B,
              AC=A*C,
              AD=A*D,
              BC=B*C,
              BD=B*D,
              CD=C*D,
              ABC=A*B*C,
              ABD=A*B*D,
              ACD=A*C*D,
              BCD=B*C*D,
              ABCD=A*B*C*D,
              y = selected_values(data_mean, A, B, C, D)[[1]],
              sd = selected_values(data_mean, A, B, C, D)[[2]]
              ) %>% ungroup() -> semi_table 

     semi_table %>% 
              mutate(xA = A*y,
                     xB = B*y,
                     xC = C*y,
                     xD = D*y,
                     xAB = AB*y,
                     xAC = AC*y,
                     xAD = AD*y,
                     xBC = BC*y,
                     xBD = BD*y,
                     xCD = CD*y,
                     xABC = ABC*y,          
                     xABD = ABD*y,
                     xACD = ACD*y,
                     xBCD = BCD*y,
                     xABCD = ABCD*y)  %>%
            summarize(TA=sum(xA)/16,
                      TB=sum(xB)/16,
                      TC=sum(xC)/16,
                      TD=sum(xD)/16,
                      TAB=sum(xAB)/16,
                      TAC=sum(xAC)/16,
                      TAD=sum(xAD)/16,
                      TBC=sum(xBC)/16,
                      TBD=sum(xBD)/16,
                      TCD=sum(xCD)/16,
                      TABC=sum(xABC)/16,
                      TABD=sum(xABD)/16,
                      TACD=sum(xACD)/16,
                      TBCD=sum(xBCD)/16,
                      TABCD=sum(xABCD)/16
                      
    ) %>% data.frame() -> qs

    qs_vector <- as.numeric(qs[1,])

    sum(qs_vector^2)*16 -> total

    (qs_vector^2*16) / total * 100 -> influ

    semi_table$y <- sprintf("%.2f", semi_table$y)
    semi_table$sd <- sprintf("%.2f", semi_table$sd)

    semi_table %>% data.frame() -> sing

    x <- c(sprintf("%.2f", qs_vector), "", "")
    f <- c(sprintf(" %.2f%% ", influ), "", "")

    result <- rbind(rbind(sing, x), f)
    return(result)
}
```

##read the results

```{r}

setwd("~/dev/machine-learning")
breast <- read_csv("result/breast/results_breast.csv", col_names = FALSE, col_types = cols(
        X27 = col_double()))
breast[2:21] <- NULL
names(breast) <- c("network","lambda","alpha","f1_mean","variance","standard_deviation","time_execution")

pima <- read_csv("result/pima/results_pima.csv", col_names = FALSE, col_types = cols(
        X27 = col_double()))
pima[2:21] <- NULL
names(pima) <- c("network","lambda","alpha","f1_mean","variance","standard_deviation","time_execution")

wine <- read_csv("result/wine/results_wine.csv", col_names = FALSE, col_types = cols(
        X37 = col_double()))
wine[2:31] <- NULL
names(wine) <- c("network","lambda","alpha","f1_mean","variance","standard_deviation","time_execution")

ionosphere <- read_csv("result/ionosphere/results_ionosphere.csv", col_names = FALSE, col_types = cols(
        X7 = col_double()))
names(ionosphere) <- c("network","lambda","alpha","f1_mean","variance","standard_deviation","time_execution")
```

## mean f1 
```{r}
breast %>% group_by(network, lambda, alpha) %>% 
         summarize(Mean_f1=mean(f1_mean), Sd=sd(f1_mean)) -> table_mean_breast

pima %>% group_by(network, lambda, alpha) %>% 
         summarize(Mean_f1=mean(f1_mean), Sd=sd(f1_mean)) -> table_mean_pima

wine %>% group_by(network, lambda, alpha) %>% 
         summarize(Mean_f1=mean(f1_mean), Sd=sd(f1_mean)) -> table_mean_wine

ionosphere %>% group_by(network, lambda, alpha) %>% 
         summarize(Mean_f1=mean(f1_mean), Sd=sd(f1_mean)) -> table_mean_ionosphere
```

## export mean f1 datasets

```{r}
write.table(table_mean_breast, "result/breast.csv", sep=",", row.names = FALSE)
write.table(table_mean_pima, "result/pima.csv", sep=",", row.names = FALSE)
write.table(table_mean_wine, "result/wine.csv", sep=",", row.names = FALSE)
write.table(table_mean_ionosphere, "result/ionosphere.csv" ,sep=",", row.names = FALSE )
```


## the best f1 
```{r}
max(table_mean_breast$Mean_f1)
max(table_mean_pima$Mean_f1)
max(table_mean_wine$Mean_f1)
max(table_mean_ionosphere$Mean_f1)
```

The best F1 measure was 0.9763564, 0.8129781, 0.9650899 and 0.9231376 for breast, pima, wine and ionosphere datasets respectively. 

## which config is the beast

```{r}
subset(table_mean_breast, Mean_f1 == max(Mean_f1)) 
subset(table_mean_pima, Mean_f1 == max(Mean_f1))
subset(table_mean_wine, Mean_f1 == max(Mean_f1))
subset(table_mean_ionosphere, Mean_f1 == max(Mean_f1))
```
The best config was always using lambda and alpha = 0.1 and the network config was 2 layers and 16 neurons for breast, 1 layers and 16 neurons for pima, 1 layers and 16 neurons for wine and 3 layers and 16 neurons for ionosphere. 


## Join datasets for ggplot 

```{r}
a <- subset(table_mean_breast, Mean_f1 == max(Mean_f1))
a['dataset'] = "Breast"
b <-subset(table_mean_pima, Mean_f1 == max(Mean_f1))
b['dataset'] = "Pima"
c <- subset(table_mean_wine, Mean_f1 == max(Mean_f1))
c['dataset'] = "Wine"
d <-subset(table_mean_ionosphere, Mean_f1 == max(Mean_f1))
d['dataset'] = "Ionosphere"

total_dataset <- rbind(a,b,c,d)
total_dataset$meta <- paste(total_dataset$lambda,"+",total_dataset$alpha)
total_dataset
```

```{r}
g <- ggplot(total_dataset, aes(x= dataset, y =Mean_f1, fill=as.factor(network))) +
geom_bar(stat = "identity", position = "dodge") +
  geom_errorbar(aes(ymin=Mean_f1-Sd, ymax=Mean_f1+Sd), width=.1) +
  labs(x ="Datasets", y = "F1 Measure Mean", fill = "Network")

g
```

Here! the plot the best f1 and config.


## sperate network column
```{r}
breast %>% separate(network, c("layers", "neurons")) -> breast
pima %>% separate(network, c("layers", "neurons")) -> pima
wine %>% separate(network, c("layers", "neurons")) -> wine
ionosphere %>% separate(network, c("layers", "neurons")) -> ionosphere
```
## 2kn table genarate 
```{r include=FALSE}
breast_2kn <- alloc_vari_4_fact(breast)
pima_2kn <- alloc_vari_4_fact(pima)
winet_2kn <- alloc_vari_4_fact(wine)
ionosphere_2kn <- alloc_vari_4_fact(ionosphere)
```



